\LARGE \bf Mean Estimation from Single-bit Measurements

### 2018-02-07 Writeups/onebit_full_V1.tex
stated working on full version

%{\color{red}  The $\mu$-sum problem (Kim-ElGamal Ch. 21) gives a lower bound. Can be reduced to the CEO.}

@@

\subsection*{Related Works}
%\subsubsection*{Statistical inference under communication constraints}
{\color{red} Shamir \cite{Shamir} showed that in hide-and-seek hypothesis testing problem, bitrate constraint may lead to a significant reduction in detection performance compared to the unrestricted case. This result is then applied to online learning, stochastic optimization and sparse PCA. Shamir's results shows that the penalty is in the dimension ($d/R$ instead of $lod(d)$). In our setting the dimension is $1$.} \\

>>>>

{\color{red} 
One-bit with constant input is important, since estimating when the parameter varies with time is always harder. Our result implies than the error in any estimation with one-bit per sample is at least $pi/2$ times the MSE with an unlimited number of bits per sample.
 \\
}

{\color{red} Check connection to the $\mu$-sum problem (Kim-ElGamal Ch. 21) that (maybe ?) gives a lower bound, and can be reduced to the CEO.
}

@@

\subsection*{Related Works}
%\subsubsection*{Statistical inference under communication constraints}
{\color{red} Shamir \cite{Shamir} showed that in hide-and-seek hypothesis testing problem, bitrate constraint may lead to a significant reduction in detection performance compared to the unrestricted case. This result is then applied to online learning, stochastic optimization and sparse PCA. Shamir's results shows that the penalty is in the dimension ($d/R$ instead of $lod(d)$). In our setting the dimension is $1$. \\
Baranuik et. al. \cite{baraniuk2017exponential} showed that adaptive one-bit measurements leads to exponential decay of MSE, but they did not consider noise!! \\
Masry and Ishwar 
\cite{masry2009field} considered the estimation of 
he case of threshold measurements of random threshold values, and provided exact expression for the mean and variance of the
error attained under two random sampling techniques and linear estimation. \\
As we explain below, our problem can also be seen as a special case of communicating a function, namely the sample mean, as in \cite{1413468}, and ($\mu$-sum).
Difference between one-bit quantization and threshold detection / quantization. 
}
